Servis: A dependently typed DSL for web APIs

### 2016-08-25 paper/paper.tex
Typos

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{minted}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\makeatletter
\renewcommand*{\thelisting}{\thesection.\arabic{listing}}
\@addtoreset{listing}{section}
\makeatother
\author{Arian van Putten \\ a.vanputten@uu.nl}
\title{Servis: A dependently typed DSL for web APIs}
\begin{document}
\maketitle
\begin{abstract}
In this paper we describe a DSL for web APIs named Servis. Servis is  inspired by Servant, a haskell type-level DSL for web APIs. We identify several issues with the current implementation of Servantm and show how Servis solves these by using features of the dependently typed language called Idris.

Specifically, we show how dependent types can help use describe dependencies within an API, how we can check at  compile time that routes in an API dont overlap, and how dependent pairs can let us verify that status codes described in an API are adhered to.

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{minted}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\makeatletter
\renewcommand*{\thelisting}{\thesection.\arabic{listing}}
\@addtoreset{listing}{section}
\makeatother
\author{Arian van Putten \\ a.vanputten@uu.nl}
\title{Servis: A dependently typed DSL for web APIs}
\begin{document}
\maketitle
\begin{abstract}
In this paper we describe a DSL for web APIs named Servis. Servis is  inspired by Servant, a haskell type-level DSL for web APIs. We identify several issues with the current implementation of Servant and show how Servis solves these by using features of the dependently typed language called Idris.

Specifically, we show how dependent types can help use describe dependencies within an API, how we can check at  compile time that routes in an API do not overlap, and how dependent pairs can let us verify that status codes described in an API are adhered to.
